---
title       : MPG Shiny App
subtitle    : Predicting a Car's MPG Based on Mtcars Data Set
author      : Xinyuan Wu
job         : Coursera Data Science
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Summary

This shiny app is based on mtcars data set. It uses four parameters to predict a car's mpg.

1. Transmission type (Automatic, Manual) 
2. Number of cylinders (4, 6, 8) 
3. Horsepower
4. Weight (1000 lbs)

```{r}
library(slidifyLibraries); library(slidify); data(mtcars); head(mtcars, n = 3)
```

---

## Mtcars Data and Pre-processing

```{r}
# convert variables to factor
mtcars$am <- factor(mtcars$am, labels = c("Auto", "Manual"))
mtcars$cyl <- as.factor(mtcars$cyl)

# select variables needed for linear fit
tidy <- mtcars[, c(9, 2, 4, 6, 1)]
head(tidy, n = 3)
```


---

## Linear Regression

The interaction between transmission type and weight is included in the linear model.

```{r}
# linear fit
fit <- lm(mpg ~ am + cyl + hp + wt + am:wt, data = tidy)
fit
```

---

## Prediction Example

```{r}
am <- "Auto"; cyl <- "6"; hp <- 150; wt <- 2.0
a <- data.frame(am = am, cyl = cyl, hp = hp, wt = wt)
mpgPred <- predict(fit, a)
```

The x coordinate value of the red vertical line is the predicted mpg.

```{r, echo = FALSE, fig.width = 10, fig.height = 5}
hist(tidy$mpg, xlab = "MPG (Miles Per Gallon)", ylab = "Frequency", col = "lightblue",
             ylim = c(0, 20), xlim = c(0, 40), breaks = 10, main = 'Histogram of MPG')
lines(c(mpgPred, mpgPred), c(0, 16), col= "red", lwd = 5)
text(15, 19, paste("MPG = ", round(mpgPred, 2)))
```

---
